Wu-Tang Clan

### 2015-03-20 rmtw/a6/latex8.tex
added intro to meth

\section{Case Company Description}
Mention the country, size and domain. 
In domain of surveillance cameras and they develop embedded software for the cameras. 
Focus mostly on the API since that's what's relevant to our study. 
Something about market leader in their domain - and that means that changes to their API could have large consequences.

@@

The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study. [Note to Richard: Do you think we can claim that our case is typical, critical, revelatory or unique? Or is our current description adequate?]

@@

\section{Methodology}

\subsection{Research strategy and investigation methods}
• Describe and explain the research strategy and investigation methods that will be used for the project. Motivate your choice? Use relevant references.
AKA EXPLAIN WHY WE DO

Brief intro, saying we will do a case study \cite{runeson2009guidelines} and what data collection methods will be used.

Explain why case study was chosen i.e. cuz we look at something in it's natural environment (it wouldn't work to look at example data)

Another reason that the case study approach was chosen is that there is little existing research conducted in the area, and that input from the industry is vital to the success of the research. (Especially to validate if the proposed ``pitfalls''  are correct).

Explain why we chose case study compared to for example design research.
%Thius might not have to be in the proposal

The goal of the study is twofold

*Define what type of goal and explain why it is ( exploratory, descriptive, explanatory, or improving.)

*It will be an embedded case study since both the code and documentation will be used as a unit of analysis. (We can discuss if interviews will be a unit of analysis or not).

>>>>

\section{Case Company Description}
The case company is a 
Mention the country, size and domain. 
In domain of surveillance cameras and they develop embedded software for the cameras. 
Focus mostly on the API since that's what's relevant to our study. 
Something about market leader in their domain - and that means that changes to their API could have large consequences.

@@

The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study. [!!!Note to Richard \#1: Do you think we can claim that our case is typical, critical, revelatory or unique? Or is our current description adequate?]

@@

\section{Methodology}
This study has been conducted using the case study methodology \cite{runeson2009guidelines}. The goal of the study was twofold. Firstly, the aim was to empirically \textit{explore} the motives behind changes to APIs, and secondly, our ambition was to \textit{validate} the results' level of correctness by comparing our findings with the case company's. Our research can be classified as an embedded case study \cite{yin2013case}, since both the API code and API documentation have used as units of analysis [!!!Note to Richard \#2: Do you agree with this?]

The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing studies \cite{runeson2009guidelines} \cite{benbasat1987case} \cite{yin2013case} \cite{robson2002real}. An alternative approach that was considered was design research, but if a ``toy program" was to be used instead of an API tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines} [!!!Note to Richard \#3: Do you think this is a valid reason? Or is it a stretch to assume that all design research involves toy programs].

An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to assess the validity of the findings related to RQ1.

We have structured our research around three major steps. Initially, the study was planned. Following that, we collected the data and lastly, we analysed the data.
